Title?

### 2019-09-26 Old/temp.tex
Work

Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
which is distributed across the secondary market via bids in local auctions. 
Buyer behavior is influenced by opponent bid profiles from multiple auctions.
The valuation of any user, however, is a function of the entire marketplace.  
We first define the ``inverse" demand for any buyer $i$,
% BUYER REVENUE 
\begin{equation}\label{buyerinversedemand}
    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
        \rho^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
\end{equation}
For a given demand $\rho^j$, $f_i$ maps the $z$th unit of data to the lowest
possible unit price. \\
\textbf{Remark:} In a coordinated bid, $f_i$ is such that
$i$ could still bid in \emph{any} auction $j\in\mcI$.
Naturally, the coordinated bid is the
lowest unit cost of the buyer to participate in all auctions, and corresponds to
the maximum reserve price amongst the sellers.

The seller is represented by a similar function, however a seller only has a
single auction, and is indirectly influenced by the buyers in other auctions, and so from the perspective of the
seller we have a more direct interpretation of revenue.
We define the ``inverse" of the buyer demand function for seller $j$ as revenue at unit price $y$. 
% SELLER REVENUE 
\begin{equation}\label{sellerinversedemand}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
\end{equation}
where $f^j$ maps to the highest possible unit data price.
Thus we have the following Lemma. 
{
\lemma{(User valuation)}\label{uservaluation}
For any buyer $i$, the valuation of seller $j$'s data may be modeled as,
\begin{equation}\label{singlevaluation}
    \theta_i^j \circ e_i^j(a) = \int_0^{e_i^j(a)} f_i(z) \ dz,
\end{equation}
it follows that 
\begin{equation}\label{buyervaluation}
    \theta_i \circ e_i(a) = \displaystyle\sum_{j\in\mcI}
 \int_0^{e_i^j(a)} f_i(z) \ dz.
\end{equation}
Similarly, seller $j$'s valuation is,
\begin{equation}\label{sellervaluation}
    \theta^j \circ e_i(a) = \displaystyle\sum_{i\in\mcI}
 \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
}
\textbf{Proof:} 
We assume that a buyer wants to minimize the cost of purchasing their data
requirement, at the same time ensuring they get the full allocation $e_i(a)$,
and so must minimally meet $j$'s reserve price.
A seller will try to maximize profit for any given allocation $a$,
and will try to sell all of its data, and so 
$d_i^j = e_i(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j = D^j =
\sum_{i\in\mcI} e_i(a)$,
The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
(THERE MUST BE A CLEARER WAY TO DESCRIBE THE RELATIONSHIP)

@@

% USER UNION
{
\lemma{(Valuation across local auctions)}\label{userunion}
For any $i,j\in \mcI$, 
\begin{equation}\label{jtoi}
j\in\mcI_i \Leftrightarrow i\in\mcI^j.
\end{equation}
Fix an auction $j\in\mcI$ and define the set of users $\Lambda$, where
\begin{equation}\label{lambda}
    \lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
\end{equation}
\begin{equation}\label{lambda}
    \Lambda = \bigcap_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg),
\end{equation}
\begin{equation}\label{lambda}
    \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
\end{equation}
and for each $i\in\mcI^j$ define,
\begin{equation}\label{ilambda}
    \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
\bigg).
\end{equation}
(WANT TO SAY $s_i^j > 0$ iff $i,j \in\Lambda \Rightarrow s_i^j \in \Lambda
\equiv s_i^j \in \mcI$)
Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$,
\begin{equation}\label{sym}
    (\theta_i \circ \theta^j) = (\theta^j \circ \theta_i).
\end{equation}
(ONLY HAVE ONE HALF OF THE SYMMETRY SO FAR! REALLY WANT TO MAKE $s_i = s^j$
HAPPEN)
}\\
\textbf{Proof:}
A local auction $j\in\mcI$, is determined by the collection of buyer bid
profiles, where $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
if and only if $p_i^j \ge p_{i^*}^j$.
Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
If $i^* \ni \mcI^j$, then (\ref{jtoi}) holds; in the latter case, by
Proposition \ref{buyerstrategy}, $i^*$
will add sellers to its pool until its demand is satisfied. Therefore for any
$j\in\mcI_i$, $\not\exists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
holds.

The subset $\mcI^j \subset \mcI$
determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
coordinated, truthful bid, $\mcI_i\subset \mcI$ 
will determine the unit price $p_{i}$ in buyer $i$'s bid.
(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
price, which in turn defines $j$'s reserve price, $p_{i^*}^j$,
the lowest price that $j$ will accept to perform any allocation.
Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
\ref{sellerstrategy},
we have that for each $i \in \mcI^j$, 
$p_{i}^j \ge p_{i^*}^j \ge p_i^k > 0$, which holds $\forall \ k \in\mcI_i$.
Let $p_*^j=p_{i^*}^j$ denote the reserve
price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
[p_i^j]_{i\ni\mcI^j}$.
Now, we have,
%Fix any buyer $i\in\mcI^j$.
\begin{equation}\label{rho}
    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
\end{equation}
and, $\forall \ i \in \mcI^j$, 
\begin{equation}\label{invrho}
    f_i \circ e_i^j(a) \ge p_*^j,
\end{equation}
and, $\forall \ k \in \mcI_i$, 
\begin{equation}\label{invrho}
    p_*^j \ge f^k \circ e_i^k(a) ,
\end{equation}
from (\ref{datademand}), (\ref{buyerinversedemand}),
(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$

The sellers $\in\Lambda$ are competing to sell
their respective resources to buyers whose valuations are distributed across multiple auctions. 
%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
Consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0$
for any $k\ne j \in \mcI_i$. 
Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we have
$\forall \ i \in \mcI^j$,
\begin{equation}\label{feq}
    p_*^j = f^j \circ e_i(a) = f_i\circ e_i(a) = p_i^*,
\end{equation}
where we denote $p_i^*$ as the coordinated bid price of buyer $i$.
Now, suppose $\exists \ i\in\mcI^j$ such that $p_i^* \ge p_*^j$.
Since,
$$
    p_i^* = \max_{k\in\Lambda_i}(f^k) \circ e_i(a)= \max_{k\in\Lambda_i}(p_*^k),
$$ 
there must be some $k \ \in\mcI_{i}$, where $p_i^k > p_*^j$, and so, 
we have that $ \Rightarrow p_i^k > p_*^j$. Also, $\not\exists$(HERE) 
It follows that buyer $i$'s bid price is given by,
\begin{equation}\label{iprice}
    p_i^j = \max_{j\in\Lambda}(f^j) \circ e_i(a)= \max_{j\in\Lambda}(p_*^j),
\end{equation}

%where $p_i^*$ represents $i$'s coordinated bid price,
%i.e., $p_i^j = p_i^*, \ \forall \ j$ such that $s_i^j > 0$.
This holds for any
$i\in\mcI^j$ and similarly if $p_i^k < p_i^j$. 
Now, from (\ref{feq}), we have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, as such, we may
denote each as $f$ in the remainder of the proof.

>>>>

Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
which is distributed across the secondary market via bids in local auctions. 
Buyer behavior is influenced by opponent bid profiles from multiple auctions.
The valuation of any user, however, is a function of the entire marketplace.  
We first define the ``inverse" demand for any buyer $i$,
% BUYER REVENUE 
\begin{equation}\label{buyerinversedemand}
    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
\end{equation}
For a given demand $\rho^j$, $f_i$ maps the $z$-th unit of data to the lowest price at
which $i$ could still bid in \emph{any} auction $j\in\mcI$.
Naturally, this is the
lowest unit cost of the buyer to participate in all auctions, and corresponds to
the maximum reserve price amongst the sellers.

The seller is represented by a similar function, however a seller only has a
single auction, and is indirectly influenced by the buyers in other auctions, and so from the perspective of the
seller we have a more direct interpretation of revenue.
We define the ``inverse" of the buyer demand function for seller $j$ as revenue at unit price $y$. 
% SELLER REVENUE 
\begin{equation}\label{sellerinversedemand}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
\end{equation}
where $f^j$ maps to the highest possible unit data price.
Thus we have the following Lemma. 
{
\lemma{(User valuation)}\label{uservaluation}
For any buyer $i$, the valuation of seller $j$'s data may be modeled as,
\begin{equation}\label{singlevaluation}
    \theta_i^j \circ e_i^j(a) = \int_0^{e_i^j(a)} f_i(z) \ dz,
\end{equation}
it follows that 
\begin{equation}\label{buyervaluation}
    \theta_i \circ e_i(a) = \displaystyle\sum_{j\in\mcI}
 \int_0^{e_i^j(a)} f_i(z) \ dz.
\end{equation}
Similarly, seller $j$'s valuation is,
\begin{equation}\label{sellervaluation}
    \theta^j \circ e_i(a) = \displaystyle\sum_{i\in\mcI}
 \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
}
\textbf{Proof:} 
We assume that a buyer wants to minimize the cost of purchasing their data
requirement, at the same time ensuring they get the full allocation $e_i(a)$,
and so must minimally meet $j$'s reserve price.
A seller will try to maximize profit for any given allocation $a$,
and will try to sell all of its data, and so 
$d_i^j = e_i(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j = D^j =
\sum_{i\in\mcI} e_i(a)$,
The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
(THERE MUST BE A CLEARER WAY TO DESCRIBE THE RELATIONSHIP)

@@

% USER UNION
{
\lemma{(Valuation across local auctions)}\label{userunion}
For any $i,j\in \mcI$, 
\begin{equation}\label{jtoi}
j\in\mcI_i \Leftrightarrow i\in\mcI^j.
\end{equation}
Fix $j\in\mcI$ and define the set of users $\Lambda$, where
\begin{equation}\label{lambda}
    \Lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
\end{equation}
and for each $i\in\mcI^j$ define,
\begin{equation}\label{ilambda}
    \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
\bigg).
\end{equation}
(WANT TO SAY $s_i^j > 0$ iff $i,j \in\Lambda \Rightarrow s_i^j \in \Lambda
\equiv s_i^j \in \mcI$)
Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$,
\begin{equation}\label{sym}
    (\theta_i \circ \theta^j) = (\theta^j \circ \theta_i).
\end{equation}
(ONLY HAVE ONE HALF OF THE SYMMETRY SO FAR! REALLY WANT TO MAKE $s_i = s^j$
HAPPEN)
}\\
\textbf{Proof:}
A local auction $j\in\mcI$, is determined by the collection of buyer bid
profiles, where $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
if and only if $p_i^j \ge p_{i^*}^j$.
Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
If $i^* \ni \mcI^j$, then (\ref{jtoi}) holds; in the latter case, by
Proposition \ref{buyerstrategy}, $i^*$
will add sellers to its pool until its demand is satisfied. Therefore for any
$j\in\mcI_i$, $\not\exists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
holds.

The subset $\mcI^j \subset \mcI$
determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
coordinated, truthful bid, $\mcI_i\subset \mcI$ 
will determine the unit price $p_{i}$ in buyer $i$'s bid.
(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
price, which in turn defines $j$'s reserve price, $p_{i^*}^j$,
the lowest price that $j$ will accept to perform any allocation.
Using (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}),
we have that for each $i \in \mcI^j$, 
$p_{i}^j \ge p_{i^*}^j \ge p_i^k > 0$, which holds $\forall \ k \in\mcI_i$.

Therefore $p_i^j \ge p_{i^*}^j, \ \forall \ i \in
[p_i^j]_{i\in\mcI^j}$. Let $p_*^j=p_{i^*}^j$ denote the reserve
price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
[p_i^j]_{i\ni\mcI^j}$.
Now, we have,
%Fix any buyer $i\in\mcI^j$.
\begin{equation}\label{rho}
    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)).
\end{equation}
using (\ref{datademand}), (\ref{buyerinversedemand}),
(\ref{sellerinversedemand}).

The sellers $\in\Lambda$ are competing to sell
their respective resources to buyers whose valuations that are distributed across multiple auctions. 
%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
Consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0$
for any $k\ne j \in \mcI_i$. 
Using (\ref{buyerinversedemand}) and
(\ref{sellerinversedemand}), 
\begin{equation}\label{feq}
    p_*^j = f_i\circ e_i(a) = f^j\circ e_i(a).
\end{equation}
Suppose for some $i\in\mcI^j \ \exists \ k \ \in\mcI_{i}$ such that $p_{i}^k > p_{*}^j$. 
%For any $k \in\Lambda_i$ we have that $p_i^k = p_i^j$. 
We have that $p_i^j = p_i^k = \max(f^k,f^j) \circ e_i(a)= \max(p_*^k, p_*^j)$.
It follows $p_i^j = p_i^k, \ \forall \ i \in \Lambda_i$,
which, for any $i\in\mcI^j$, holds $\forall \ k\in\mcI_i$.
It follows that buyer $i$'s bid price is given by,
\begin{equation}\label{iprice}
    p_i^j = \max_{j\in\Lambda}(f^j) \circ e_i(a)= \max_{j\in\Lambda}(p_*^j),
\end{equation}
%where $p_i^*$ represents $i$'s coordinated bid price,
%i.e., $p_i^j = p_i^*, \ \forall \ j$ such that $s_i^j > 0$.
and so $p_i^j = p_i^k > 0, \ \forall \ k \in \mcI_i$.

This holds for any
$i\in\mcI^j$ and similarly if $p_i^k < p_i^j$. 
Now we have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, as such, we may
denote each as $f$ in the remainder of the proof.
